---
title: "Evaluation of Craft Breweries in the <br> United States of America <br>"
author: "<br>Heindel Adu, Amy Markmum and Gabriel Gonzalez <br>- AGH Data Consult Inc."
date: "Spring 2019"
output:
  html_document:
    highlight: pygments
    keep_md: yes
    theme: united
    always_allow_html: yes
  pdf_document: default
---
#
#<br>
#

#### Load the necessary library packages prior to loading the data. 
#### Packages used include : 
####   <em>  -tidyr
####   <em>  -dplyr
####   <em>  -plotly
####      -plotly
####      -forcats 

```{r setup, include=FALSE}
library(tidyr)
library(dplyr)
library(plotly)
library(forcats)
library(ggmap)
library(maps)
library(ggplot2)

register_google(key = 'AIzaSyBODcDvf37-5ae26FN1Oe5uStngqlccrXc')
```
# <br>
##### 1. Read the beers data file Beers.csv and inspect the dataframe (head and tail).

```{r}
library(readr)
Beers <- read_csv("Beers.csv")
head(Beers)
```

```{r}
tail(Beers)
```

##### 2. Read the breweries data file Breweries.csv and inspect the dataframe (head and tail).
```{r}
library(readr)
Breweries <- read_csv("Breweries.csv")
```
```{r}
head(Breweries)
```

```{r}
tail(Breweries)
```
##### 3. Inspect the data structures, rename columns that make sense and prepare to join the data sets. Joining could be accomplished with a left, right or full join. Full join is used in this case to preserve data from both tables.
```{r}
str(Breweries)
```

```{r}
str(Beers)
```
```{r}
names(Breweries)
```
##### Renamed Brewery_id to match the Brew_ID inthe Breweries dataset.
```{r}
names(Beers)
```
```{r}
Beers <- rename(Beers, Brew_ID = Brewery_id)
names(Beers)
```
##### Full join method.
```{r}
fullData <- full_join(Breweries, Beers, by = "Brew_ID")
```

```{r}
head(fullData)
```
##### Another column renaming is needed to correct the data names after the join. 
```{r}
fullData <- rename(fullData, BreweryName = Name.x, BeerName = Name.y)
names(fullData)
```
```{r}
fullData %>%
  group_by(State) %>%
  summarise(count = n())%>%
  arrange(desc(count))
```
##### Exploring the number of breweries in each state, the Breweries.csv data is used. Grouped the Breweries data table by states.
```{r}
BrewStatesC <- Breweries%>%
  group_by(State)%>%
  summarise(count = n())%>%
  arrange(desc(count))
```

```{r}
head(BrewStatesC)
```
```{r}
state.freq <- table(Breweries$State)
barplot(state.freq[order(state.freq)], 
        horiz = T,
        border = NA,
        xlim = c(0, 100),
        main = "Number of Breweries per State",
        xlab = "Number of Brewiews",
        ylab = "States")
```
#<br> 
# Counting the number of brewweries in each state:

```{r}
head(state.freq)
```

```{r}
sDF<-data.frame(state.freq) 
sDF<- rename(sDF, State = Var1, Brew_Count=Freq)
```

#<br>

##### Plot the number of breweries in each state.

```{r}
p1 <- ggplot(Breweries, aes(x = fct_rev(fct_infreq(State)), fill = fct_infreq(State))) + geom_bar() + coord_flip() + theme(axis.title.x=element_blank(),                                                                                                                   axis.title.y=element_blank(),legend.position = "none")


ggplotly(p1)  
```

##### Plot the number of beer brands from each state.

```{r}
p2 <- ggplot(fullData, aes(x = fct_rev(fct_infreq(State)), fill = fct_rev(fct_infreq(State)))) + geom_bar()  + theme(legend.position = "none") +
  labs( title = "", x = "none", y = "Count of Beer") + theme(axis.title.x=element_blank(),                                                                                                                   axis.title.y=element_blank(),legend.position = "none")

ggplotly(p2)
```

##### Did we have any empty rows in our data tables? Let's find out here:

```{r}
naB_Id<-sum(is.na(fullData$Brew_ID))
naB_Nm<-sum(is.na(fullData$BreweryName))
naB_C<-sum(is.na(fullData$City))
naB_S<-sum(is.na(fullData$State))
naBeer_Nm<-sum(is.na(fullData$BeerName))
naBeer_Id<-sum(is.na(fullData$Beer_ID))
naABV<-sum(is.na(fullData$ABV))
naIBU<-sum(is.na(fullData$IBU))
naStyle<-sum(is.na(fullData$Style))
naOunces<-sum(is.na(fullData$Ounces))


naResults = paste(naB_Id, naB_Nm, naB_C, naB_S, naBeer_Nm, naBeer_Id, naABV, naIBU, naStyle, naOunces, sep = ", ")

print(naResults)
```
```{r}
names(fullData)

```

```{r}
select(fullData, State, ABV, IBU)

```
```{r}
Breweries %>%
  group_by(State) %>%
  tally(sort = TRUE)
```
```{r}
fullData %>%
  group_by(State) %>%
  summarise(state_count = n()) %>%
  arrange(desc(state_count))
```

```{r}
mFD <- fullData %>%
  group_by(State) %>%
  summarise_each(funs(mean), mean_ABV = ABV, mean_IBU = IBU) %>%
  arrange(desc(mean_ABV))
```

```{r}
ggplot(fullData, aes(x = ABV)) + 
  geom_bar(na.rm = T) + 
  theme_grey() + 
   coord_flip()
```
```{r}
p11<-ggplot(fullData, aes(x = IBU, fill = "red")) + 
  geom_bar(na.rm = T) + 
  scale_color_brewer("Blues")
ggplotly(p11)
```

```{r}
fullData %>%
  group_by(State) %>%
  summarise_each(funs(min, max), ABV) 
```

```{r}
mFDt<- data.frame(fullData %>%
  group_by(State) %>%
  summarise ( min_ABV =min(ABV), mean_ABV = mean(ABV), max_ABV = max(ABV)) %>%
  arrange(desc(max_ABV)))
```

```{r}
mIBU<- fullData %>%
  group_by(State) %>%
    summarise (min_IBU =min(IBU), mean_IBU = mean(IBU), max_IBU = max(IBU)) %>%
  arrange(desc(max_IBU))
```


```{r}
fullData %>%
    group_by(BreweryName) %>%
    summarise ( min_IBU =min(IBU), mean_IBU = mean(IBU), max_IBU = max(IBU)) %>%
  arrange(desc(max_IBU))
```
```{r}
coef(lm(IBU ~ ABV, data = fullData))
```



#### Colored by State
```{r}
ggplot(fullData, aes(ABV, IBU, colour = State)) +
     geom_point(na.rm = T) +
  geom_abline(intercept = -34.09865, slope = 1282.037)
```
```{r}
ggplot(fullData, aes(ABV, IBU, colour = ABV)) +
     geom_point(aes(colour = ABV), na.rm = T) +
  geom_abline(intercept = -34.09865, slope = 1282.037)
```
#### Color by state
```{r}
ggplot(fullData, aes(ABV, IBU, colour = State)) +
  facet_wrap(~ State) +
    geom_point(na.rm = T) +
  geom_abline(intercept = -34.09865, slope = 1282.037) 
```
#### Color by alcohol volume

```{r}
ggplot(fullData, aes(ABV, IBU, colour = State)) +
  facet_wrap(~ State) +
    geom_point(aes(colour = ABV),na.rm = TRUE) +
  geom_abline(intercept = -34.09865, slope = 1282.037)
```


```{r}
ggplot(fullData, aes(ABV, IBU, colour = State)) +
  facet_wrap(~ Style) +
    geom_point(aes(colour = ABV),na.rm = TRUE) +
  geom_abline(intercept = -34.09865, slope = 1282.037)
```

```{r}
ggplot(fullData, aes(State, ABV)) +
  geom_boxplot(na.rm = T)
```
```{r}
ggplot(fullData, aes(State, IBU)) +
  geom_boxplot(na.rm = T) 
```

```{r}
ggplot(fullData, aes(ABV, IBU, colour = ABV)) +
     geom_point(aes(colour = ABV), na.rm = T) +
  geom_abline(intercept = -34.09865, slope = 1282.037) + 
  geom_smooth(method = lm, se = T, na.rm = T)
```
#####Density map of ABV vs IBU. 
```{r}
dplot<-ggplot(fullData, aes(ABV, IBU, colour = ABV)) +
     geom_point( na.rm = T)

dplot + stat_density_2d(aes(fill= ..level.., alpha = 0.75 ) , na.rm = T, geom = "polygon")
```

